---
title: "Analysis of Control Signal and Wheel Speed of Permobil C500"
author: "Charles"
date: "September 22, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r envir, echo=FALSE, message=FALSE, warning=FALSE}
setwd("C:/Study/Coursera/1 Data-Science/2 RStudio/9 Class 9/Coursera_DataScience_Class9_DataProduct")
library(plotly)
library(dplyr)
```

## Introduction

Electric Wheelchair Permobil C500 uses two signals to control the speed of two wheels, thus control the movement
of the wheelchair.
These two signals are "Forward/Backward" (as "FB") and Right/Left (as "RL").
The range for both signals is from 4.5 V to 7.5 V.
In order to estimate the movement of wheelchair for research experiment purpose, we need to know the relationship
between these two signals and the wheel speed (rpm).

We use 0.5 V as a interval to change these two signals from 4.5 V to 7.5 V separately, and measure the speed of wheel three times per combination to get the data.
Then fit a linear regression model to get the coefficients.
So we can set these two signals to estimate the path trajectory of the wheelchair.

## Data Set

The column "FB" and "RL" are the input signal Forward/Backward" and "Right/Left".
The column "RWSpeed" and "LWSpeed" are the speed of right wheel and left wheel in rpm.
Data set looks like this:

```{r dataset, cache=TRUE, echo=FALSE}
data <- read.csv("Experiment_Data.csv", header = TRUE)
dataWheel <- data[2:nrow(data),] %>%
        select(1:4) %>%
        'colnames<-'(c("FB","RL","RW","LW")) %>%
        mutate(RWSpeed = as.numeric(as.character(RW)) * 4) %>%
        mutate(LWSpeed = as.numeric(as.character(LW)) * 4)
```
```{r show data}
head(dataWheel)
str(dataWheel)
```

## Plot

```{r fit linear model, echo=FALSE, cache=TRUE}
fitRight <- lm(RWSpeed ~ as.numeric(as.character(FB)) + as.numeric(as.character(RL)), data = dataWheel)
fitLeft <- lm(LWSpeed ~ as.numeric(as.character(FB)) + as.numeric(as.character(RL)), data = dataWheel)
dataWheel2 <- mutate(dataWheel, SpeedR=predict(fitRight,dataWheel)) %>%
                mutate(speedL=predict(fitLeft,dataWheel))
```


```{r plot right, echo=FALSE}
gRight <- plot_ly(data = dataWheel2, x=~FB, y=~RWSpeed, color = ~RL,
                  type = "scatter", mode = "lines+markers",
                  line = list(dash="dash"),
                  hoverinfo = 'text',
                  text = ~paste('</br> Forward/Backward(V): ', FB,
                                '</br> Left/Right(V): ', RL,
                                '</br> RightWhellSpeed(rpm): ', RWSpeed)) %>%
        add_trace(y=~SpeedR, mode = "lines", line = list(width=4, dash=""), showlegend = FALSE) %>%
        layout(title = "Right Wheel speed with two signals",
                xaxis = list(title = "Forward/Backward(V)"),
                yaxis = list (title = "Right Wheel speed(rpm)"))
gRight
```

```{r plot left, echo=FALSE}
gLeft <- plot_ly(data = dataWheel2, x=~FB, y=~LWSpeed, color = ~RL,
                  type = "scatter", mode = "lines+markers", line = list(dash="dash"),
                 hoverinfo = 'text',
                  text = ~paste('</br> Forward/Backward(V): ', FB,
                                '</br> Left/Right(V): ', RL,
                                '</br> RightWhellSpeed(rpm): ', LWSpeed)) %>%
        add_trace(y=~speedL, mode = "lines", line = list(width=4, dash=""), showlegend = FALSE) %>%
        layout(title = "Left Wheel speed with two signals",
                xaxis = list(title = "Forward/Backward(V)"),
                yaxis = list (title = "Left Wheel speed(rpm)"))
gLeft
```







































